---
title: "Cannabis_P"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,fig.height = 8,fig.width = 10)
```

```{r , include=FALSE}
library('tidyverse')
library('tidytext')
library("ggraph")
library('igraph')
library("extrafont")
library("highcharter")
fonts()
theme_set(theme_minimal())

```

## Data loading +  Cleaning

Available on <a>https://www.kaggle.com/kingburrito666/cannabis-strains</a>

```{r }

data <- read_csv(here::here(file = "cannabis.csv"))%>%
        janitor::clean_names()

```



```{r}
data_separate <- data %>%
  separate_rows(effects, sep = ",")%>%
  separate_rows(flavor , sep = ",")%>%
  filter(!is.na(flavor))
  
```

```{r}
data_separate %>%
  count(flavor,sort = TRUE)


data_separate %>%
  count(effects , sort = TRUE)
```

## What is the effect of flavor on the rating of the cannabis ? 
```{r}

data_separate %>%
  group_by(flavor)%>%
  summarise(avg_rating = mean(rating,na.rm = TRUE),
            count = n()) %>%
  arrange(desc(avg_rating)) %>%
  ungroup()%>%
  mutate(flavor = fct_reorder(flavor , avg_rating))%>%
  ggplot(mapping = aes(x = flavor , y = avg_rating))+
  geom_point(size = 1.5)+
  coord_flip()+
  labs(x = "Flavor" , y = "Average Rating" , title= "Influence of flavor on the rating")
```


## Let's try to do the same but with the effect of the strain , we will also look on the type of the strain cause certain customer expect different effect from certain type of strain


```{r}
library('tidytext')

data_separate %>%
  group_by(type,effects)%>%
  summarise(avg_rating = mean(rating),
            count = n())%>%
  filter(count >= 100) %>%
  arrange(desc(avg_rating)) %>%
  ungroup() %>%
  mutate(effects = reorder_within(effects , avg_rating,type,sep = ":"))%>%
  ggplot(mapping = aes(x = effects , y = avg_rating,fill = factor(effects)))+
  geom_col()+
  coord_flip()+
  facet_wrap(~type , scales = "free_y")+
  expand_limits(y = 0)+
  theme(legend.position = "") + 
  scale_x_reordered()+
  labs(y = "Average Rating" , x = "Effects",title  = "What most effects people like in certain type of cannabis")+
  scale_y_continuous(breaks = seq(0,5,0.5))
```





```{r}



features <- data_separate %>%
  filter(flavor!= "Nonne" ,effects != "None")%>%
  select(-c(description))%>%
  mutate(effects = as.factor(effects),
         flavor = as.factor(flavor),
         type = as.factor(type),
         value_1 = 1 ,
         value_2 = 1,
         value_3 = 1)%>%
  pivot_wider(names_from = effects,values_from = value_1)%>%
  pivot_wider(names_from = flavor , values_from = value_2)%>%
  pivot_wider(names_from = type , values_from = value_3)%>%
  unnest()%>%
  mutate_if(is.double,function(x) ifelse(is.na(x),0,x))%>%
  mutate_at(vars(-rating),as.factor)




library("caret")

lassoGrid <- expand.grid(alpha = 1, lambda = seq(0.001,0.1,by = 0.0005))
model <- train(rating~.-strain, data = features , method = "glmnet",tuneGrid =lassoGrid ,metric  ="Rsquared")

library('broom')


tidy(model$finalModel) %>%
  filter(term != "(Intercept)")%>%
  mutate(term = fct_reorder(term , estimate,sum))%>%
  ggplot(mapping = aes(x = term , y =estimate,fill = estimate > 0))+
  geom_col()+
  coord_flip()+
  theme_minimal()

colnames(features) <- make.names(colnames(features))

```



### Clustering Cannabis flavor and effect


```{r}

library("widyr")

effect_cor <- data_separate%>%
  mutate(flavor_effect = paste0(effects,"_",flavor))%>%
  add_count(effects,sort = TRUE)%>%
  filter(n >=300)%>%
  pairwise_cor(effects,strain,sort = TRUE)

```



```{r}

fill_color = c("#ffca28","#0288d1")

effect_cor %>%
  group_by(item1)%>%
  top_n(10,correlation)%>%
  ungroup()%>%
  mutate(item2 = reorder_within(item2,correlation,item1))%>%
  ggplot(mapping = aes(correlation,item2,fill = correlation > 0))+
  geom_col()+
  facet_wrap( ~item1,scales = "free_y")+
  scale_y_reordered()+
  labs(x = "" , y = "" , title = "Corrélation entre les effets du cannabis" , fill = "Corrélation positive ? ")+
  theme_dark()+
  theme(plot.background = element_rect(fill = "#34495e"),
        legend.background = element_rect(fill = "#34495e"),
        axis.text = element_text(colour = "#f0f3f4",family = "Arial Nova Light"),
        legend.position = "",
        plot.title = element_text(colour = "#f0f3f4",family = "Segoe UI",hjust = 0.45,size = 14))+
  scale_fill_manual(values = fill_color)

```


  

### Perform a PCA

```{r}

data_separate %>%
  mutate(value = 1)%>%
  widely_svd(effects,strain,value)%>%
  filter(dimension <=6) %>%
  group_by(dimension)%>%
  top_n(10,abs(value))%>%
  ungroup()%>%
  mutate(effects = reorder_within(effects,value,dimension))%>%
  ggplot(mapping = aes(value,effects,fill = value > 0))+
  geom_col()+
      scale_y_reordered()+
  facet_wrap(~dimension,scales = "free")
```




### Let's do some interactive graph

Inspired by a kaggler (Owen Ouyang)
```{r}

one <- data %>%
  group_by(name = type , drilldown = type)%>%
  summarise(y = n())%>%
  arrange(desc(y))

two <- data_separate %>%
  group_by(type,effects)%>%
  mutate(y = n())%>%
  arrange(desc(y))%>%
  group_by(name = type , id  =type) %>%
  do(data = list_parse(
    mutate(.,name = effects , drilldown =tolower(paste(type,effects,sep = ":")) )%>%
    group_by(name,drilldown)%>%
    summarise(y = n())%>%
    select(name,y,drilldown) %>%
    arrange(desc(y))
  ))


highchart() %>% 
  hc_chart(type = 'bar') %>% 
  hc_xAxis(type = "category",labels = list(style = list(color = "white"))) %>% 
  hc_add_series(name = 'Nombre de cannabis', data = one,colorByPoint = TRUE) %>% 
  hc_drilldown(
    allowPointDrilldown = TRUE,
    series =list_parse(two)
  ) %>%
  hc_legend(enabled = F) %>% 
  hc_title(text = "Les effets de chaque type de cannabis")%>%
  hc_add_theme(hc_theme_google())
```



